### 2019-04-24 README.Rmd
small readme update
updated readme

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Overt attentional capture by reward-related stimuli overcomes top-down suppression"
```

@@

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Overt attentional capture by reward-related stimuli overcomes inhibitory suppression"
```

@@

[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch)
